Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd

 riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
 cols = c("white", "Purple", "blue", "orange")
 rectangles$shade[rectangles$shade == "Highlight"] = riksplace
 rectangles$shade = factor(rectangles$shade)

@@

\begin{figure}
\begin{tabular}{cccccc}
\includegraphics[width=2cm,height=2cm]{aka.png}&
\includegraphics[width=1cm,height=1cm]{HY-CC.png}&
\includegraphics[width=1cm,height=1cm]{kansalliskirjasto.png}&
\includegraphics[width=1cm,height=1cm]{kungliga.png}&
\includegraphics[width=1cm,height=1cm]{github-logo.png}
\end{tabular}
\end{figure}

>>>>

 riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
 cols = c("white", "Purple", "yellow", "orange")
 rectangles$shade[rectangles$shade == "Highlight"] = riksplace
 rectangles$shade = factor(rectangles$shade)

@@

\begin{figure}
\begin{tabular}{cccccc}
\includegraphics[width=2cm,height=2cm]{aka.png}&
\includegraphics[width=1cm,height=1cm]{HY-CC.png}&
\includegraphics[width=1cm,height=1cm]{kansalliskirjasto.png}&
\includegraphics[width=1cm,height=1cm]{kungliga.png}&
\includegraphics[width=1cm,height=1cm]{github-logo.png}&
\includegraphics[width=1cm,height=1cm]{Rlogo.png}
\end{tabular}
\end{figure}
